Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-29 paper_v1.Rnw
First satisfaction results

@@

@@

TODO Sherif adds satisfaction analyses here

>>>>

<<loadcsv, echo=FALSE>>=
#library(RCurl)
#data <- getURL("https://raw.githubusercontent.com/whynotyet/MOOC_dropout/master/compiled_data_all_courses.csv", ssl.verifypeer=0L, followlocation=1L)
#a = read.csv(text=data)
a = read.csv("C:/Research/Analytics/pycode/user_code/halawa/publications/LAS2015/data_masters/compiled_data_all_courses.csv")

# Shift scores for satisfaction index components up to 1-N
a$qoe = a$qoe + 4
a$satis_amount_learnt = a$satis_amount_learnt + 4
a$satis_vs_time_spent = a$satis_vs_time_spent + 4
a$satis_time_mgmt = a$satis_time_mgmt + 4
a$how_met_expectations = a$how_met_expectations + 3
a$how_engaging_material_presentation = a$how_engaging_material_presentation + 1

satM = subset(a, select=c('qoe', 'satis_amount_learnt', 'satis_vs_time_spent', 'how_met_expectations', 'how_engaging_material_presentation'))
a$satisfaction = rowMeans(satM, na.rm=TRUE)
a$satisfaction[!is.finite(a$satisfaction)] = NA

library(plyr)
a$did_dropout = revalue(factor(a$did_dropout), c("0"="No", "1"="Yes"))
@

@@

<<test1, echo=TRUE>>=
@

@@

First, we compared the distributions of satisfaction scores for learners who reported they stopped participating and those who reported not to have stopped. As figure \ref{fig:study1_satis_si_score_dist_comparison} shows, the mean satisfaction score ($mean=4.70$) for learners who reported to have stopped is 0.64 points lower than the other group ($mean=5.34$).

<<study1_satis_si_score_dist_comparison, echo=FALSE, fig.env='figure*', fig.pos='ht', fig.height=4, fig.width=9, fig.cap='Satisfaction index scores for learners who reported they stopped / did not stop participating before end of course'>>=
y0 = a$satisfaction[a$did_dropout == "No"]
y1 = a$satisfaction[a$did_dropout == "Yes"]
b = a[!is.na(a$did_dropout),]
ggplot(b) + geom_boxplot(aes(x=b$did_dropout,y=b$satisfaction)) + theme_bw() + labs(y="Satisfaction",x="Stopped participating?")
@
